The problem and promise of scale in multilayer animal social networks

### 2020-02-13 paper/manuscript.Rmd
refs

The integration of behavioural and ecological theory has shown the value of
considering the importance of various ecological disciplines to better
understand and predict animal social networks, including demography (Shizuka and
Johnson 2019), evolutionary and quantitative genetics (Fisher and McAdam 2017),
disease ecology (Silk et al. 2017), and animal personality (Sih et al. 2017).
While the number of studies integrating social network theory into a broader
array of behavioural and ecological sub-disciplines is impressive, only recently
has the role of animal space use been considered in describing the causes and
consequences of the social environment in the context of (1) phenotypes and
individual fitness [@Webber_2018], (2) movement ecology and collective movement
[@Bode_2011], and (3) habitat selection and space use [@He_2019]. Importantly,
much of the work linking space use and the social environment has been
theoretical and empirical studies are lacking (but see Peignier et al. 2019;
Pinter-Wollman 2015; Strandburg-Peshkin et al. 2015; 2017). Here, we discuss the
role mutlilayer networks within the emerging integration of social and spatial
ecology within the behavioural ecology literature.

>>>>

The integration of behavioural and ecological theory has shown the value of
considering the importance of various ecological disciplines to better
understand and predict animal social networks, including demography
[@Shizuka_2019], evolutionary and quantitative genetics [@Fisher_2017], disease
ecology [@Silk_2017], and animal personality [@Sih_2018]. While the number of
studies integrating social network theory into a broader array of behavioural
and ecological sub-disciplines is impressive, only recently has the role of
animal space use been considered in describing the causes and consequences of
the social environment in the context of (1) phenotypes and individual fitness
[@Webber_2018], (2) movement ecology and collective movement [@Bode_2011], and
(3) habitat selection and space use [@He_2019]. Importantly, much of the work
linking space use and the social environment has been theoretical and empirical
studies are lacking [but see @Peignier_2019;
@Strandburg_Peshkin_2015; @Strandburg_Peshkin_2017]. Here, we discuss the role
mutlilayer networks within the emerging integration of social and spatial
ecology within the behavioural ecology literature.
